---
title: "linear model from Web"
author: "Jaelynn Schultz"
date: "Summer 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```


```{r}
basicNN + geom_point()
```
This scatter plot exhibits a positive linear relationship between SIMS and ARM. Essentially, this means that those workers with greater arm strength performed better on the simulations that were utilized to measure job performance. The greater the arm strength, the better their simulation performance. 

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
This value shows the exact correlation coefficient on the relationship between arm strength and simulation performance. This value, 0.686, is a pretty significant number that lends itself to a positive linear relationship between SIMS and ARM.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
The first model above shows the linear model of the relationship between SIMS and ARM. Of the information listed above, the most essential is the residual standard error and the adjusted R-square value. At 1.226, the residual standard error exhibits that the values do not differ significantly from the predicted value. In addition to this, the value of the adjusted R-square value means we are dropping the error from the mean model by 46.6%.

#### Predict at target point


#### scatterplot with model fit
  

## Model 2 SIM~GRIP

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

