---
title: "linear model from Web"
author: "Jaelynn Schultz"
date: "Summer 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```


```{r}
basicNN + geom_point()
```
This scatter plot exhibits a positive linear relationship between SIMS and ARM. Essentially, this means that those workers with greater arm strength performed better on the simulations that were utilized to measure job performance. The greater the arm strength, the better their simulation performance. 

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
This value shows the exact correlation coefficient on the relationship between arm strength and simulation performance. This value, 0.686, is a pretty significant number that lends itself to a positive linear relationship between SIMS and ARM.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
The first model above shows the linear model of the relationship between SIMS and ARM. Of the information listed above, the most essential is the residual standard error and the adjusted R-square value. At 1.226, the residual standard error exhibits that the values do not differ significantly from the predicted value. In addition to this, the value of the adjusted R-square value means we are dropping the error from the mean model by 46.6%.

#### Predict at target point

```{r}
Targetpoint <- data.frame(ARM = 88, GRIP = 94)
```

```{r}
predict(model.1, Targetpoint, interval = "prediction")
```
This data predicts the value we would find in model 1 if the target point for ARM was 88 and GRIP was 94. However, this data only shows a use for the target point of ARM. It disregards GRIP. 


#### scatterplot with model fit
  
```{r}
basicNN + geom_point() + geom_lm()
```
This model now features the prediction line that was interpreted in previous models. It proves that the relationship results in a normal distribution, which 95% of the points are within two residual values from the line. 

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
basicGRIP <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basicGRIP + geom_point()
```
Again, there appears to be a positive linear relationship between SIMS and GRIP. The greater GRIP strength of a worker, the better they perform on the simulation. 

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```
This value shows the specific correlation coefficient on the relationship between SIMS and GRIP. Still a significant number at 0.639 to show a positive linear relationship between SIMS and GRIP, it is not as high as the number shown in the first model. 

### Inferential  (Build model.2)
  
```{r}
model.2 <- lm(SIMS~GRIP, data=data)
summary.lm(model.2)
``` 
Shown above is the linear model of the relationship exclusively between GRIP and SIMS. Like the last model, this also shows the standard residual standard error value and the adjusted R-squared. In comparison, we should expect that the standard deviation curve on this model will be wider than the previous model. The adjusted R-squared value on this values also means that we can reduce the error from the mean model by 40.53%. This percentage is lower than that of the first model, however. Majority of the error is still explained by the first model. 

#### predict model.2 at target point

```{r}
predict(model.2, Targetpoint, interval = "prediction")
```

#### now add the model fit to our plot for model.2
  
```{r}
basicGRIP + geom_point() + geom_lm()
```
This scatter plot has combined the original data with predicted values for SIM-GRIP. All information considered, this model is not so reliable as arm strength in predicting a worker's performance in the simulations. 

## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
The value of the correlation coefficient of the third model appears to be larger then either of the previous two. This shows that this model may overall be better than the first two models, but additional testing can be conducted to confirm this. 
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP, data=data)
summary.lm(model.3)
``` 
The model featured above shows the relationship of between SIMS, ARM, and GRIP altogether. According to the residual standard error and adjusted R-squared values, this model appears to be considerably better than the prior two models. The residual standard error is lower on this model, meaning the standard deviation curve should be more narrow. Additionally, the adjusted R-squared value is higher in comparison to the other two models, meaning this model could reduce up to 53.58% of error from the mean model. This show significantly better results than the previous two models which only showed relationships between ARM and GRIP to SIMS respectively. 

#### predict model.3 at target point
  
```{r}
predict(model.3, Targetpoint, interval = "prediction")
```

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova(model.1, model.3)
``` 
The anova test above offers that model 1 has a residual standard error of 217.88, while model 3 has a residual standard error of 188.43. This means that model 3 reduced the residual standard error of model 1 by 29.45. In addition to this, the p-value shows that this is statistically significant. As such, we can conclude confidently that model 3 is superior to model 1. 

### Model.2 vs Model.3

```{r}
anova(model.2, model.3)
``` 
Based on this anova test, we can see that model 2 has a residual standard error of 243.07 and model 3 has a residual standard error of 188.43. This means that model 3 reduced the residual standard error of model 2 by 54.639. Again, the p-value shows that this is statistically significant. As such, we can once again confidently confirm that model 3 is better than model 2. 

## Informally compare Model.1 with model.2

```{r}
anova(model.2, model.1)
```
In the final anova model above, the order of the models is switched so as to ensure that the difference in RSS value would show the better model. As such, we can see that model 2 on this test, which is actually model 1, is the better model.